Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
cite Mesaros

\subsubsection*{Participation to the DCASE 2016 challenge}
In order to evaluate how general our findings are, we have taken part in the acoustic scene classification task 2016 edition of the DCASE challenge, whose results are forthcoming.
This edition relies on the TUT 2016 acoustic scenes dataset, which contains $15$ classes of acoustic scenes, and is larger than the DCASE 2013 private dataset by one order of magnitude

>>>>

\subsubsection*{Participation to the DCASE 2016 challenge}
In order to evaluate how general our findings are, we have taken part in the acoustic scene classification task 2016 edition of the DCASE challenge, whose results are forthcoming.
This edition relies on the TUT 2016 acoustic scenes dataset, which contains $15$ classes of acoustic scenes, and is larger than the DCASE 2013 private dataset by one order of magnitude \cite{Mesaros2016_EUSIPCO}.
